---
title: "Depression Analysis"
author: "Mburu Moses"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## 

```{r}

library(tidyverse)
library(data.table)
library(ggthemes)
library(knitr)
train <- setDT(read.csv("train.csv"))

test <- setDT(read.csv("test.csv"))

```

## Combining train and test for easier processing


```{r}

train[, sample := "train"]

test[, sample := "test"]

depression_dat <- rbindlist(list(train,test))


depression_dat[sample == "train", .N, by = .( depressed)] %>%
    .[, .( depressed,perc = round(N/sum(N) * 100, 2))] %>%
    kable()



```


##

```{r}

naVals <- colSums(is.na(depression_dat))/nrow(depression_dat) * 100 

withNa <- naVals[naVals>0]

missing_perc <- data.table(variables = names(withNa), perc = withNa) 


```

##

```{r}
ggplot(missing_perc, aes( reorder(variables, perc), perc))+
    geom_bar(stat = "identity") +
    theme_fivethirtyeight()+
    coord_flip()
```

##

We can see that most variables with missing information are related to medical variabes. We can start by investigating the missingnes to see
* is the data missing at random
* is there sytematic missingness
We should also try to see if missing data means something else such us 0 incase of variables like med_u5_deaths	Proportion of children <5 who died (1 year)


```{r}
missing_vars <- names(withNa)

missing_vars_df <- depression_dat[, ..missing_vars]

col_types <- sapply(missing_vars_df, class)

missing_vars_dfm <- melt(missing_vars_df, id.vars = "depressed")

missing_vars_dfm %>% .[, .(mean_var = mean(value, na.rm = T), 
                          median_var = median(value, na.rm = T),
                          min_var = min(value, na.rm = T),
                          max_var = max(value, na.rm = T),
                          perc_miss = round(sum(is.na(value)/.N *100),2 )), by = variable] %>%
    kable()
```


